---
title: "SRS-ICC"
output: html_notebook
author: "Qianying Wu"
---
Calculating the ICC of the SRS scores, including total score, subscale scores, and item-wise scores.


#First import libraries
```{r library}
library(tidyverse)
library(ggplot2)
library(psych)
library(ggpubr)
setwd("/Users/wuqy0214/Documents/GitHub/SRS_variability_stability/code") # change to your own directory
```

#Load data
```{r load_data}
data_trt <- read_csv("../data/test_retest_excl",col_names = TRUE)[,-1]
```

# ICC calculation
Helper function: calculate ICC of one variable
Input: the variable name
Output: ICC, upper bound, lower bound

```{r helperF}
ICC_var_calculate <- function(varname,data){
  # extract variables
  data_var <- data[,c(paste0(varname,"_T1"),paste0(varname,"_T2"))]
  
  # calculate ICC: two-way random effects, absolute agreement, single measurement ICC(2,1)
  suppressMessages({ICC_result <- ICC(data_var)})
  output <- ICC_result$results[,c("ICC","upper bound","lower bound")][2,]
  
  return(output)
}

```

Calculate ICC for online and In-lab sample, respectively, for the period after the cutoff

```{r ICC_onlinevsinlab,  message=FALSE, warning=FALSE}
# all variables
var_list <-  c("SRS","SRS_AWR","SRS_COG","SRS_COM","SRS_MOT","SRS_RRB",paste0("SRS_",seq(1,65)))
# output
ICC_all_types <- data.frame()

data_lab = data_trt[data_trt$format=="In lab",]
for (varname in var_list){
  # calculate ICC
  res_var <- ICC_var_calculate(varname,data_lab)
  res_var$variable = varname
  res_var$gap = "six-mo"
  res_var$sample = "In lab"
  # combine results to the dataframe
  ICC_all_types <- rbind(ICC_all_types,res_var)
}

data_online = data_trt[data_trt$format=="Online",]
for (varname in var_list){
  # calculate ICC
  res_var <- ICC_var_calculate(varname,data_online)
  res_var$variable = varname
  res_var$gap = "six-mo"
  res_var$sample = "Online"
  # combine results to the dataframe
  ICC_all_types <- rbind(ICC_all_types,res_var)
}
```
Calculate the combined ICC

```{r ICC_ALL,  message=FALSE, warning=FALSE}
# all variables
var_list <-  c("SRS","SRS_AWR","SRS_COG","SRS_COM","SRS_MOT","SRS_RRB",paste0("SRS_",seq(1,65)))
# output
ICC_all <- data.frame()

for (varname in var_list){
  # calculate ICC
  res_var <- ICC_var_calculate(varname,data_trt)
  res_var$variable = varname
  res_var$gap = "six-mo"
  res_var$sample = "both"
  # combine results to the dataframe
  ICC_all <- rbind(ICC_all,res_var)
}

write.csv(ICC_all, "../results/ICC_both.csv", row.names=FALSE, quote=FALSE) 

```

# Visualization
Make plots to visualize the results
1. all short term vs. long term 
2. in lab: short term vs. long term
3. long term: in lab vs. online
4. all in lab vs. online

We want to reorder the variables so the figure looks more intuitive
```{r helperF_reorder0}
reorder_vars <- function(data,data_order){
  subscales <- c("SRS_AWR", "SRS_COG", "SRS_COM", "SRS_MOT", "SRS_RRB")
  data <- data %>%
    mutate(variable = factor(variable, 
                             levels = c(
                               setdiff(data$variable, c("SRS", subscales))[order(data_order$ICC[!(data$variable %in% c("SRS", subscales))], decreasing = FALSE)],  # Finally, the rest in descending order of 'ICC',
                               subscales[order(data_order$ICC[match(subscales, data$variable)], decreasing = FALSE)], # then order by subscales
                              "SRS"  # First, always put 'SRS' on top
                               )
                             )
           )
  return(data)
}
```



```{r vis_online_vs_inlab,fig.width=3,fig.height=5}
ICC_lab = filter(ICC_all_types, sample == "In lab")
ICC_lab <- reorder_vars(ICC_lab,ICC_lab)
ICC_online = filter(ICC_all_types, sample == "Online")
ICC_online <- reorder_vars(ICC_online,ICC_lab)

ggplot() + 
  # all lab
  geom_point(data=ICC_lab, aes(x = variable, y = ICC), color = "orange", shape = 16, size = 2) +  # Represent the mean values
  geom_errorbar(data=ICC_lab, aes(x = variable, y = ICC, ymin = `lower bound`, ymax = `upper bound`), color = "orange", width = 0.2) +  
  # all online
  geom_point(data=ICC_online, aes(x = variable, y = ICC), color = "blue",shape = 16, size = 2) +  # Represent the mean values
  geom_errorbar(data=ICC_online, aes(x = variable, y = ICC, ymin = `lower bound`, ymax = `upper bound`), color = "blue",width = 0.2) +  
  labs(x = "Variable", y = "ICC (95% CI)", title = "Lab vs. Online (no exclusion)") +
  geom_hline(yintercept = 0.75, color="red")+
  coord_flip()+
  theme_minimal()+
  theme(axis.text.y = element_text(size=6))

# save ICC_lab and ICC_online
write.csv(ICC_lab, "../results/ICC_lab.csv", row.names=FALSE, quote=FALSE) 
write.csv(ICC_online, "../results/ICC_online.csv", row.names=FALSE, quote=FALSE) 
```